Gene expression

### 2022-11-22 code/Gene expression.Rmd
Returning to Imac

>>>>

## Statistical analysis of dCT levels 
```{r}
anova <- delta_gene_expr %>% 
  group_by(genes) %>% 
  anova_test(dct ~ groups) %>% 
  ungroup()

significant <- delta_gene_expr %>% 
  group_by(genes) %>% 
  do(lm(dct ~ groups,.) %>%  tidy) %>% 
  filter(term != "(Intercept)") %>% 
  filter(p.value <= 0.05)
```

## Add house gene to list
```{r}
wide_genes <- delta_gene_expr %>% 
  select(sample_id,ct_value_house_gene_HRPT, groups, genes, dct) %>% 
  pivot_wider(id_cols = c("sample_id","groups","ct_value_house_gene_HRPT"), names_from = genes, values_from = dct) %>% 
  mutate(HRPT = ct_value_house_gene_HRPT) 
```

## TAble
```{r}
Exp4_genes_table <- delta_gene_expr %>% 
  select(sample_id,ct_value_house_gene_HRPT, groups, genes, dct) %>% 
  pivot_wider(id_cols = c("sample_id","groups","ct_value_house_gene_HRPT"), 
              names_from = genes, 
              values_from = dct) %>% 
  mutate(
    HRPT = ct_value_house_gene_HRPT)  %>% 
  select(
    -sample_id, -ct_value_house_gene_HRPT) %>% 
  tbl_summary(by = groups,
              digits = everything() ~ c(1,1),
              missing = "no",
              #include = !"INFg",
              #type = all_continuous() ~ "continuous2",
              statistic = all_continuous() ~ ("{mean} ({sd})")) %>%
  modify_header(
    label ~ "**Groups:**") %>% 
   #modify_footnote(stat_1 ~ "Median (IQR)", stat_2 ~ "p-value on overall group differences,Kruskall-Wallis rank sum test ") %>% 
add_p(everything() ~ "aov") %>% 
  as_gt() %>%
  tab_header(title = md("**Gene expression** *(dCT values)*")) %>%
  opt_align_table_header("center") %>% 
   tab_options(heading.title.font.size = 15,
               heading.background.color = "lightgrey",
               ) %>% 
     tab_source_note(
    source_note = "HRPT served as reference gene."
  )

Exp4_genes_table %>% 
  gtsave(path = "exports/genes/", filename = "Exp4-gene-dct-table-aov.png")
```
